---
title: "Part 1 - stringr functions"
author: "Grace Brofman"
date: "2/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```
### Detect string patterns with "str_detect()"
for any entry that contains that pattern anywhere within it - only returns t/f
```{r}
vec <- c(" A Unicorn    Fish ", "add   cornmeal", "French FRIES", "acorn Squash")

str_detect(vec, pattern = "corn") #returns True of False for each of the 4 elements
# (t,t,f, t)

```

using the start wars dataset - add filter() to keep rows where the pattern we're looking for shows up in that column (in this case 'walk')
```{r}
walk_subset <- starwars %>% 
  filter(str_detect(name, pattern = "walk")) # only for lowercase walk

# Use str_subset as a combo of filter()/str_detect()

```

### Replace a string pattern with something else
'str_replace()' to replace an existing string pattern with something else.

```{r}
# anywhere 'corn' shows up, replace it with "COOL"
vec_bren <- str_replace(vec, pattern = "corn", replacement = "COOL")
vec_bren

```

replace the patter "Sky" with the pattern "TORNADO"
```{r}
sw_tornado <- starwars %>% 
  mutate(name = str_replace(name, pattern = "Sky", replacement = "TORNADO"))
# overwriting column by keeping name as name

```

## Use 'str_trim()' to remove excess leading and trailing whitespace

```{r}
str_trim(vec)

#str_squish removes leading and trailing whitespace, and also looks for repreated interior whitespace to reduce to one

str_squish(vec)

```

```{r}
str_detect(vec, pattern = "Corn") # returns nothing because R is case-sensitive, so "Corn" is different form "corn"

```

- str_to_*()    * = case you want to convert your string to
```{r}
str_to_lower(vec)

str_to_upper(vec)

str_to_title(vec)

```

Using these in combination:
```{r}
# 1. filter to only contain observations where the name column contains the string pattern "Darth" 
# 2. use mutate and str_replace to replace "Darth" with "LLAMA"
# 3. use mutate to convert name column to all lowercase
sw_combo <- starwars %>% 
  filter(str_detect(name, pattern = "Darth")) %>% 
  mutate(name = str_replace(name, pattern = "Darth", replacement = "LLAMA")) %>% 
  mutate(name = str_to_lower(name)) 

  

```











